### 2012-09-10 demo/taxize.Rmd
updated tutorial to recent changes...

### Get a tree in newick format, read using ape::read.tree, and plot
```{r}
tree <- get_phylomatic_tree(mytree, 'TRUE', 'POST', 'new', 'FALSE')
treephylo <- read.tree(text = tree)
plot(treephylo)
```

@@

## Show higher taxonomy for a given TSN
```{r}
classification(685566)
```

## Get a TSN from a sepcies name
```{r}
get_tsn("Quercus_douglasii", "sciname", by_="name")
```

@@

# Using ITIS and Phylomatic together 
## Use ITIS and get_phymat_format to format a string for each species to be submitted to Phylomatic
```{r}
dat_ <- laply(list("36616", "19322", "183327"), get_phymat_format, format='rsubmit')
dat_
dat_mine <- paste(dat_, collapse="%0D%0A") # collapse and replace \n's
dat_mine
tree <- get_phylomatic_tree(dat_mine, 'FALSE', 'GET', 'new', 'TRUE')
tree
plot(tree)
```

## A somewhat realistic workflow
### User's species list 
```{r}
splist <- c("annona_cherimola", 'annona_muricata', "quercus_robur", 
						"shorea_robusta", "pandanus_patina", "oryza_sativa", "durio_zibethinus")
```

### Get TSN code for each species
```{r}
tsns <- laply(splist, get_tsn, searchtype = "sciname", by_ = "name")
tsns
```

### Get Phylomatic formatted strings for each species
```{r}
dat_ <- laply(tsns, get_phymat_format, format='rsubmit')
dat_
```

@@

### Plot tree, etc. 
```{r}
plot(tree)
```

>>>>

### Get a tree in newick format, read using ape::read.tree, and plot
```{r phylog1 }
tree <- get_phylomatic_tree(mytree, 'TRUE', 'POST', 'new', 'FALSE')
treephylo <- read.tree(text = tree)
plot(treephylo)
```

@@

## Show higher taxonomy for a given TSN
```{r}
classification(685566, ID="tsn")
```

## Get a TSN from a sepcies name
```{r}
get_tsn(searchterm = "Quercus_douglasii", searchtype = "sciname")
```

@@

# Using ITIS and Phylomatic together 
## Use ITIS and get_phymat_format to format a string for each species to be submitted to Phylomatic
```{r phylog2}
dat_ <- laply(list("36616", "19322", "183327"), get_phymat_format, format='rsubmit')
dat_
dat_mine <- paste(dat_, collapse="%0D%0A") # collapse and replace \n's
dat_mine
tree <- get_phylomatic_tree(dat_mine, 'FALSE', 'GET', 'new', 'TRUE')
tree
plot(tree)
```

## A somewhat realistic workflow
### User's species list 
```{r}
splist <- c("annona cherimola", 'annona muricata', "quercus robur", 
						"shorea robusta", "pandanus patina", "oryza sativa", "durio zibethinus")
```

### Get TSN code for each species
```{r}
tsns <- get_tsn(splist, "sciname")
tsns
```

### Get Phylomatic formatted strings for each species
```{r}
dat_ <- laply(tsns, get_phymat_format, format = 'rsubmit')
dat_
```

@@

### Plot tree, etc. 
```{r phylog3}
plot(tree)
```
